\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual Multi-Loop Integrands

### 2023-09-21 notes/2loopNLSM.tex
CK fix and box ordering
small edit

\begin{figure}
\centering
{\MCutC, \MCutD, \sumoCut, \MCutJ,  
 \\
  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
\\
\MCutI,  \MCutE, \MCutK, 
\\
 \MCutL, \MCutG,  \MCutH
}
\caption{The 14 non-pathological four-point two-loop cubic diagrams.} \label{fig:MaxCuts}
  \end{figure}
What we have just been described is
sometimes referred to as ``global'' color-kinematics duality because
the Jacobi identities are solved by a single (global) integrand with
off-shell internal lines.  In order to perform the double copy it is
enough to simply satisfy the Jacobi identities on the generalized
unitarity cuts, meaning that each graph can be assigned its own ansatz
\cite{Bern:2015ooa}.  If a global solution cannot be found, this is
one way to enlarge the ansatz where the other option described above
was to incorporate non-local terms in the ``numerators''.  A globally
color-dual integrand is desirable because of its simplicity and
because a color-dual Lagrangian would naively produce precisely this
object.

@@

The final constraints comes from ensuring that the ansatz correctly
reproduces the generalized unitarity cuts of the desired theory, thus
guaranteeing that the numerators encode the correct physical,
theory-dependent information.  Generalized unitarity methods has been
reviewed in many places so we will be light on details here
\cite{BCFUnitarity, Bern:2015ooa, Bourjaily:2017wjl,
  JJHenrikReview, FivePointN4BCJ, Bern:2012uf, BCJreview,
  Edison:2022jln, Edison:2022smn}, which was recently optimized for effective field theories like NLSM \cite{Carrasco:2023qgz}. Generalized unitarity equates products of on-shell tree amplitudes,
encoded via a graph $\gamma$, to sums over compatible\footnote{A
  diagram $g$ is compatible with the cut diagram $\gamma$ if $g$ is
  isomorphic to $\gamma$ or to any of the additional factorization
  channels of $\gamma$. } diagram numerators evaluated on the support
of the on-shell conditions and weighted by their uncut propagators
\begin{equation}
\label{eq:SchematicCutEquation}
\text{Cut}[\gamma]= \sum_{\substack{\text{states}\\\text{crossing } E(\gamma)}} \prod_{v \in V(\gamma)} \atree(v)
= \sum_{g \text{ compat } \gamma}
\frac{N[g] \vert_\text{cut}}{\prod \limits_{\text{uncut}} \ell^2}
 \, ,
\end{equation}
where $V(\gamma)$ are the vertices of $\gamma$ and $E(\gamma)$ its
edges.  The sum over states hides much of the complexity of cut
construction: for scalars the process is trivial while spinning states
greatly complicate matters (see
Refs.~\cite{Kosmopoulos:2020pcd,Edison:2022jln} for recent discussion
and detailed examples of evaluating state sums).  As an example of the
two types of expressions appearing in \cref{eq:SchematicCutEquation},
consider the so-called iterated two-particle cut which can be
represented as a product of trees via
\begin{equation}
  \label{eq:example-cut-prod}
  \ExCutLabeled{1}{2}{3}{4} = \!\!\!\!\! \sum_{\substack{\text{states of }\\ \{\ell_1, \ell_2, \ell_3, \ell_4\}}} \!\!\!\!\!\!\!
  \atree(1,2,\ell_1,\ell_2) \atree(-\ell_1,-\ell_2,\ell_3,\ell_4) \atree(-\ell_3,-\ell_4,3,4)
\end{equation}
or as a collection of diagram numerators via
\begin{align}
  \label{eq:example-cut-sum}
  \ExCutLabeled{1}{2}{3}{4} &=
  \frac{\delta(\textcolor{cut-color}{\ell_1^2})
    \delta(\textcolor{cut-color}{\ell_2^2})
    \delta(\textcolor{cut-color}{\ell_3^2})
    \delta(\textcolor{cut-color}{\ell_4^2})}{(\textcolor{ucp-color}{\ell_5})^2
    (\textcolor{ucp-color}{\ell_6})^2
    (\textcolor{ucp-color}{\ell_7})^2}
  \ N\left[
    \IUCContrib{1}{4}{3}{2}{\ell_5}{\ell_6}{\ell_7}
                              \right] \notag \\
  &\quad + 
  \frac{\delta(\textcolor{cut-color}{\ell_1^2})
    \delta(\textcolor{cut-color}{\ell_2^2})
    \delta(\textcolor{cut-color}{\ell_3^2})
    \delta(\textcolor{cut-color}{\ell_4^2})}
    {(\textcolor{ucp-color}{\ell_5})^2
    (\textcolor{ucp-color}{\ell_6})^2
    (\textcolor{ucp-color}{\ell_7'})^2}
  \ N\left[
    \IUCContrib{1}{3}{4}{2}{\ell_5}{\ell_6}{\ell_7'}
    \right] + 25\text{ others.}
\end{align}
When drawing cut diagrams, we will use gray blobs as in the left-hand
sides of \cref{eq:example-cut-prod,eq:example-cut-sum} and all drawn
legs are assumed to be on-shell.  When drawing numerator contributions
to cuts, we will not use blobs on vertices, and will use
\textcolor{cut-color}{dashed lines} bisecting edges to denote cut
lines and use colored edges to highlight the
\textcolor{ucp-color}{uncut propagators}.  From now on we will leave
the cut $\delta(\ell^2)$s implicit.

>>>>

\begin{figure}
\centering
{\MCutC, \MCutD, \sumoCut, \MCutJ,  
 \\
  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
\\
\MCutI,  \MCutE, \MCutK, 
\\
 \MCutL, \MCutG,  \MCutH
}
\caption{The 14 non-pathological four-point two-loop cubic diagrams.} \label{fig:MaxCuts}
  \end{figure}
What we have just described is
sometimes referred to as ``global'' color-kinematics duality because
the Jacobi identities are solved by a single (global) integrand with
off-shell internal lines.  In order to perform the double copy it is
enough to simply satisfy the Jacobi identities on the generalized
unitarity cuts, meaning that each graph can be assigned its own ansatz
\cite{Bern:2015ooa}.  If a global solution cannot be found, this is
one way to enlarge the ansatz where the other option described above
was to incorporate non-local terms in the ``numerators''.  A globally
color-dual integrand is desirable because of its simplicity and
because a color-dual Lagrangian would naively produce precisely this
object.

@@

The final constraints comes from ensuring that the ansatz correctly
reproduces the generalized unitarity cuts of the desired theory, thus
guaranteeing that the numerators encode the correct physical,
theory-dependent information.  Generalized unitarity methods has been
reviewed in many places so we will be light on details here
\cite{BCFUnitarity, Bern:2015ooa, Bourjaily:2017wjl,
  JJHenrikReview, FivePointN4BCJ, Bern:2012uf, BCJreview,
  Edison:2022jln, Edison:2022smn}, which was recently optimized for effective field theories like NLSM \cite{Carrasco:2023qgz}. Generalized unitarity equates products of on-shell tree amplitudes,
encoded via a graph $\gamma$, to sums over compatible\footnote{A
  diagram $g$ is compatible with the cut diagram $\gamma$ if $g$ is
  isomorphic to $\gamma$ or to any of the additional factorization
  channels of $\gamma$. } diagram numerators evaluated on the support
of the on-shell conditions and weighted by their uncut propagators
\begin{equation}
\label{eq:SchematicCutEquation}
\text{Cut}[\gamma]= \sum_{\substack{\text{states}\\\text{crossing } E(\gamma)}} \prod_{v \in V(\gamma)} \atree(v)
= \sum_{g \text{ compat } \gamma}
\frac{N[g] \vert_\text{cut}}{\prod \limits_{\text{uncut}} \ell^2}
 \, ,
\end{equation}
where $V(\gamma)$ are the vertices of $\gamma$ and $E(\gamma)$ its
edges.  The sum over states hides much of the complexity of cut
construction: for scalars the process is trivial while spinning states
greatly complicate matters (see
Refs.~\cite{Kosmopoulos:2020pcd,Edison:2022jln} for recent discussion
and detailed examples of evaluating state sums).  As an example of the
two types of expressions appearing in \cref{eq:SchematicCutEquation},
consider the so-called iterated two-particle cut which can be
represented as a product of trees via
\begin{equation}
  \label{eq:example-cut-prod}
  \ExCutLabeled{1}{2}{3}{4} = \!\!\!\!\! \sum_{\substack{\text{states of }\\ \{\ell_1, \ell_2, \ell_3, \ell_4\}}} \!\!\!\!\!\!\!
  \atree(1,2,\ell_1,\ell_2) \atree(-\ell_1,-\ell_2,\ell_3,\ell_4) \atree(-\ell_3,-\ell_4,3,4)
\end{equation}
or as a collection of diagram numerators via
\begin{align}
  \label{eq:example-cut-sum}
  \ExCutLabeled{1}{2}{3}{4} &=
  \frac{\delta(\textcolor{cut-color}{\ell_1^2})
    \delta(\textcolor{cut-color}{\ell_2^2})
    \delta(\textcolor{cut-color}{\ell_3^2})
    \delta(\textcolor{cut-color}{\ell_4^2})}{(\textcolor{ucp-color}{\ell_5})^2
    (\textcolor{ucp-color}{\ell_6})^2
    (\textcolor{ucp-color}{\ell_7})^2}
  \ N\left[
    \IUCContrib{1}{4}{3}{2}
                              \right] \notag \\
  &\quad + 
  \frac{\delta(\textcolor{cut-color}{\ell_1^2})
    \delta(\textcolor{cut-color}{\ell_2^2})
    \delta(\textcolor{cut-color}{\ell_3^2})
    \delta(\textcolor{cut-color}{\ell_4^2})}
    {(\textcolor{ucp-color}{\ell_5})^2
    (\textcolor{ucp-color}{\ell_6})^2
    (\textcolor{ucp-color}{\ell_7'})^2}
  \ N\left[
    \IUCContrib{1}{3}{4}{2}
    \right] + 25\text{ others.}
\end{align}
When drawing cut diagrams, we will use gray blobs as in the left-hand
sides of \cref{eq:example-cut-prod,eq:example-cut-sum} and all drawn
legs are assumed to be on-shell.  When drawing numerator contributions
to cuts, we will not use blobs on vertices, and will use
\textcolor{cut-color}{dashed lines} bisecting edges to denote cut
lines and use colored edges to highlight the
\textcolor{ucp-color}{uncut propagators}.  From now on we will leave
the cut $\delta(\ell^2)$s implicit.
